MSDS6371Project

### 2020-11-23 MSDS6371Project.Rmd
adjust rmd

#write a program to generate 5 different combination to test forward selection model
iterations = 5
splitPerc = 0.9
total_RMSE = 0
for(i in 1:iterations){
  print(i)
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  forward_fit = lm(lSalePrice~.-Id,data=train)
  forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
  prediction = predict(forward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#total RMSE = 0.1235978... 
total_RMSE/iterations

>>>>

#write a program to generate 5 different combination to Cross-Validate Forward Selection Model
iterations = 5
splitPerc = 0.9
total_RMSE = 0
for(i in 1:iterations){
  print(i)
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  forward_fit = lm(lSalePrice~.-Id,data=train)
  forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
  prediction = predict(forward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#total RMSE = 0.1235978... 
total_RMSE/iterations
